---
title: "Codes for making figures for Archive of Pathology Paper"
output: html_document
author: "Run Jin"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R codes to generate figure
# Note that the code does not include the data read in files - the files are stored in local directories. Therefore, this file would not be able to display in knitr.

```{r setup}
install.packages(tidyverse)
library(tidyverse)
```

Read in the excel file and gathre information of target 1 and target 2 Ct values:

```{r}
NxTAG_lowP_gather <- NxTAG_lowP %>% gather(target_id, ct_values, c(Target1_Ct, Target2_Ct))
NxTAG_cons_gather <- NxTAG_cons %>% gather(target_id, ct_values, c(Target1_Ct, Target2_Ct))
abbott_lowP_gather <- abbott_lowP %>% gather(target_id, ct_values, c(Target1_Ct, Target2_Ct))
abbott_cons_gather <- abbott_cons %>% gather(target_id, ct_values, c(Target1_Ct, Target2_Ct))
```

Factors are re-leveled to put "positive" first. New categories are added to mark those files for later combination:

```{r}
NxTAG_lowP_gather$NxTAG_results <- factor(NxTAG_lowP_gather$NxTAG_results, levels = c("Positive", "Negative"))
NxTAG_cons_gather$NxTAG_results <- factor(NxTAG_cons_gather$NxTAG_results, levels = c("Positive", "Negative"))

abbott_lowP_gather$Abbott_results <- factor(abbott_lowP_gather$Abbott_results, levels = c("Positive", "Negative"))
abbott_cons_gather$Abbott_results <- factor(abbott_cons_gather$Abbott_results, levels = c("Positive", "Negative"))

NxTAG_lowP_gather <- NxTAG_lowP_gather %>% mutate(category = "lowP")
NxTAG_cons_gather <- NxTAG_cons_gather %>% mutate(category = "Cons")
abbott_cons_gather <- abbott_cons_gather %>% mutate(category = "Cons")
abbott_lowP_gather <- abbott_lowP_gather %>% mutate(category = "lowP")
```

Generate plots. 
```{r}
ggplot(NxTAG_lowP_gather, aes(x = NxTAG_results, y = ct_values, color = NxTAG_results)) + geom_boxplot() + geom_jitter(shape = 16, size = 2, position = position_jitter(0.2)) + facet_grid( . ~ target_id) + ylim(15,40) + scale_fill_manual(values=c("red", "blue")) +scale_color_manual(values=c("red", "blue")) + theme_bw()

ggplot(NxTAG_cons_gather, aes(x = NxTAG_results, y = ct_values, color = NxTAG_results)) + geom_boxplot() + geom_jitter(shape = 16, size = 2, position = position_jitter(0.2)) + facet_grid( . ~ target_id) + ylim(15,40) + scale_fill_manual(values=c("red", "blue")) +scale_color_manual(values=c("red", "blue")) + theme_bw()

ggplot(abbott_cons_gather, aes(x = Abbott_results, y = ct_values, color = Abbott_results)) + geom_boxplot() + geom_jitter(shape = 16, size = 2, position = position_jitter(0.2)) + facet_grid( . ~ target_id) + ylim(15,40) + scale_fill_manual(values=c("red", "blue")) +scale_color_manual(values=c("red", "blue")) + theme_bw()

ggplot(abbott_lowP_gather, aes(x = Abbott_results, y = ct_values, color = Abbott_results)) + geom_boxplot() + geom_jitter(shape = 16, size = 2, position = position_jitter(0.2)) + facet_grid( . ~ target_id) + ylim(15,40) + scale_fill_manual(values=c("red", "blue")) +scale_color_manual(values=c("red", "blue")) + theme_bw()

```

Different datasets with the same testing methods are combined to generate a combined figure.
```{r}
NxTAG_all_gather <- bind_rows(NxTAG_lowP_gather, NxTAG_cons_gather)
NxTAG_all_gather$full_cat <-paste(NxTAG_all_gather$NxTAG_results, NxTAG_all_gather$category, sep = "_")

abbott_all_gather <- bind_rows(abbott_lowP_gather, abbott_cons_gather)
abbott_all_gather$full_cat <-paste(abbott_all_gather$Abbott_results, abbott_all_gather$category, sep = "_")

ggplot(abbott_all_gather, aes(x = Abbott_results, y = ct_values, color = full_cat))  + geom_boxplot() + geom_jitter(shape = 16, size = 2, position = position_jitter(0.2)) + facet_grid( . ~ target_id) + ylim(15, 40) + scale_fill_manual(values=c("red", "#037f51", "blue", "purple")) +scale_color_manual(values=c("red", "#037f51", "blue", "purple")) + theme_bw()

ggplot(NxTAG_all_gather, aes(x = NxTAG_results, y = ct_values, color = full_cat))  + geom_boxplot() + geom_jitter(shape = 16, size = 2, position = position_jitter(0.2)) + facet_grid( . ~ target_id) + ylim(15, 40) + scale_fill_manual(values=c("red", "#037f51", "blue", "purple")) +scale_color_manual(values=c("red", "#037f51", "blue", "purple")) + theme_bw()
```

